### 2011-04-05 docs/enthalpy/enthalpy.tex
Add a little more commentary.
More about comparison of current extra terms to volume discrepancy factor.

Now writing $e = e(p,T,X_k)$ and expanding $De/Dt$ and using the energy evolution equation:
\begin{equation}
\rho \frac{D e}{Dt}  = \rho \left( e_p \frac{D p}{Dt} + e_T \frac{D T}{Dt} + \sum_k e_{X_k} \frac{D X_k}{Dt} \right)
                     = -p \nabla \cdot \Ub + \rho \Hnuc
\end{equation}
we can express $DT/Dt$ in terms of 
\begin{eqnarray*}
\frac{DT}{Dt} &=& \frac{1}{\rho e_T} \left(
                  -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
\end{eqnarray*}
where $e_T = \left.\partial e/\partial T\right|_{p,X_k}$ is the
specific heat at constant volume,
and $e_p = \left.\partial e/\partial p\right|_{T,X_k}.$
Then
\begin{equation}
-\rho \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( \frac{D p}{Dt} 
    - \frac{p_T}{\rho e_T} \left(
                 -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}
which leads to 
\begin{equation}
\left(-\rho -  \frac{p p_T}{\rho e_T p_\rho} \right) \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( (1 + \frac{e_p p_T}{e_T}) \frac{D p}{Dt} 
                           - \frac{p_T}{\rho e_T} \left(
                                        \rho \Hnuc
                                        - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}

@@

The second equation subtracted from the first gives:
\begin{equation}
  \left \{ \frac{Dp_0}{Dt} - \frac{Dp}{Dt} \right \} + (p - p_0)  \nabla \cdot \Ub
\end{equation}

@@

\item When we stay on the constraint, i.e. $p_{EOS} = p_0$, then the equations for $e$ and
for $h$ are identical.   However, once we are off the constraint, do the terms in the
current evolution equation for $h$ serve to drive us back to the constraint?  Recall
our current "volume discrepancy factor" acts as a source term which modifies the
divergence constraint, which effectively modifies both $\rho$ and $T$ (or $e$ or $h$).
The term in the enthalpy equation only modifies $\rho.$  Is this relevant and/or useful??

>>>>

Now writing $e = e(p,T,X_k)$ and expanding $De/Dt$ and using the energy evolution equation:
\begin{equation}
\rho \frac{D e}{Dt}  = \rho \left( e_p \frac{D p}{Dt} + e_T \frac{D T}{Dt} + \sum_k e_{X_k} \frac{D X_k}{Dt} \right)
                     = -p \nabla \cdot \Ub + \rho \Hnuc
\end{equation}
we can express $DT/Dt$ in terms of 
\begin{eqnarray*}
\frac{DT}{Dt} &=& \frac{1}{\rho e_T} \left(
                  -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
\end{eqnarray*}
where $e_T = \left.\partial e/\partial T\right|_{p,X_k}$ 
and $e_p = \left.\partial e/\partial p\right|_{T,X_k}.$
Then
\begin{equation}
-\rho \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( \frac{D p}{Dt} 
    - \frac{p_T}{\rho e_T} \left(
                 -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}
which leads to 
\begin{equation}
\left(-\rho -  \frac{p p_T}{\rho e_T p_\rho} \right) \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( (1 + \frac{e_p p_T}{e_T}) \frac{D p}{Dt} 
                           - \frac{p_T}{\rho e_T} \left(
                                        \rho \Hnuc
                                        - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}
Note that we can replace $p$ by $p_0$ in the coefficient on the l.h.s. as well as on the r.h.s.

@@

The second equation subtracted from the first gives:
\begin{equation}
  -\frac{D (p - p_0)}{Dt} + (p - p_0)  \nabla \cdot \Ub
\end{equation}

@@

\item When we stay on the constraint, i.e. $p_{EOS} = p_0$, then the equations for $e$ and
for $h$ are identical.   However, once we are off the constraint, do the terms in the
current evolution equation for $h$ serve to drive us back to the constraint?  Recall
our current "volume discrepancy factor" acts as a source term which modifies the
divergence constraint, which effectively modifies both $\rho$ and $T$ (or $e$ or $h$).
The term in the enthalpy equation only modifies $\rho.$  Is this relevant and/or useful??
Recall that the current "volume discrepancy factor" takes the form of adding 
to the r.h.s. of the constraint:
\begin{equation}
\nabla \cdot(\beta_0\Ub) = \beta_0\left(S-\frac{1}{\overline{\Gamma_1} p_0}
       \frac{\partial p_0}{\partial t} - \frac{f}{\overline{\Gamma_1} p_0}
       \frac{p_0-p_\text{EOS}}{\dt}\right) 
\end{equation}
